Holomorphic field theories and higher algebra

### 2024-09-20 draft.tex
adding bw stuff AGAIN

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
We briefly recall the approach to this regulation scheme.

>>>>

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
We briefly recall the approach to this regulation scheme.
